\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-11 fully-abstract-comp/popl2019/paper.tex
Reformulation

\section{Proving full abstraction}
\label{sec:fa-proof}
%\todo[inline]{Write small introduction. Maybe something about the difficulty of full-abstraction proofs (with references?) but mention that this is easier than some other cases (reference approximate back translation?) because back translation is trivial.}
% \begin{itemize}
% \item Logical relation
% \item FTLR
% \item Sketch high-level structure of the proof
% \end{itemize}
The backbone of the full-abstraction proof is a cross language, step-indexed, Kripke logical relation.
It relates the observable behavior of \srccm{} to the observable behavior of \trgcm{}.
In the full-abstraction proof, it allows us to transfer termination assumptions between the two machines which enables the use of a contextual equivalence assumption.
We first give an informal presentation of the logical relation before we return to a sketch of the full-abstraction proof.

@@

\subsubsection{Code region}
The code region is a central region to the logical relation that models the code memory of a component.
It is especially interesting because its seal interpretation function specifies what the return and closure seals in a component can seal.
The code region is defined as follows:
\[
  \codereg{\sigrets,\sigcloss,\mscode,\gc} \defeq (\pure,
  H^\mathrm{code,\square} \; \sigrets \; \sigcloss \; \mscode \; \gc,
  H^\mathrm{code}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc)
\]
The code region is $\pure$ which makes it persistent in future worlds and reflects the fact that it is addressed by normal capabilities.
The memory relation $H^\mathrm{code,\square} \; (\dots)$ only relates $\mscode$ to itself which agrees with our component setup where code memory is read-only.
$H^\mathrm{code,\square} \; (\dots)$ requires $\mscode$ to be well-formed and that its contents is non-linear and in the value relation.
As we will see later, we have two value relations: a trusted and an untrusted.
The value relation used depends on whether the code region governs trusted or untrusted code.
For now it suffices to know that the untrusted value relation contains everything that untrusted code can safely have, and the trusted value relation includes everything that is in the untrusted value relation in addition to the things that are not safe to pass away in a call, e.g.\ return seals.

@@

\subsubsection{Value relations}
The purpose of the value relations is twofold: It relates the words on \srccm{} to the words they correspond to on \trgcm{}, and it defines what pairs of words are safe, i.e.\ are unable to break the guarantees of the capability machines including the LSE and WBCF guaranteed by \srccm{}.
As previously explained, we try to ensure LSE and WBCF for some trusted code that we expect to behave well, e.g.\ by treating return seals in a reasonable way.
This means that it is safe to give return seals to trusted code; but at the same time, we have some code that we do not trust and that we want to guarantee LSE and WBCF against.
This means that there is a difference between what is safe to give to the trusted code and the untrusted code which we capture by having a trusted and untrusted value relation.
The two value relations are sketched in Figure~\ref{fig:value-relation}.

>>>>

\section{Proving full abstraction}
\label{sec:fa-proof}
%\todo[inline]{Write small introduction. Maybe something about the difficulty of full-abstraction proofs (with references?) but mention that this is easier than some other cases (reference approximate back translation?) because back translation is trivial.}
% \begin{itemize}
% \item Logical relation
% \item FTLR
% \item Sketch high-level structure of the proof
% \end{itemize}
The backbone of the full-abstraction proof is a cross-language, step-indexed, Kripke logical relation.
It relates the observable behavior of \srccm{} to the observable behavior of \trgcm{}.
In the full-abstraction proof, it allows us to transfer termination assumptions between the two machines which enables the use of a contextual equivalence assumption.
We first give an informal presentation of the logical relation before we return to a sketch of the full-abstraction proof.

@@

\subsubsection{Code region}
The code region is a central region to the logical relation that models the code memory of a component.
It is especially interesting because its seal interpretation function specifies what the return and closure seals in a component can seal.
The code region is defined as follows:
\[
  \codereg{\sigrets,\sigcloss,\mscode,\gc} \defeq (\pure,
  H^\mathrm{code,\square} \; \sigrets \; \sigcloss \; \mscode \; \gc,
  H^\mathrm{code}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc)
\]
The code region is $\pure$ which makes it persistent in future worlds and reflects the fact that it is addressed by normal capabilities.
The memory relation $H^\mathrm{code,\square} \; (\dots)$ only relates $\mscode$ to itself which agrees with our component setup where code memory is read-only.
$H^\mathrm{code,\square} \; (\dots)$ requires $\mscode$ to be well-formed and that its contents is non-linear and in the value relation.
As we will see later, we have two value relations: a trusted and an untrusted.
The value relation used depends on whether the code region governs trusted or untrusted code.
For now it suffices to know that the untrusted value relation contains everything that untrusted code can safely have, and %the trusted value relation contains the untrusted value relation and the things that are not safe to pass away in a call, e.g.\ return seals.
the untrusted value relation is subsumed in the trusted value relation that also includes the things that are not safe to pass away in a call, e.g.\ return seals.

@@

\subsubsection{Value relations}
The purpose of the value relations is twofold: It relates the words on \srccm{} to the words they correspond to on \trgcm{}, and it defines what pairs of words are safe, i.e.\ are unable to break the guarantees of the capability machines including the LSE and WBCF guaranteed by \srccm{}.
As previously explained, we try to ensure LSE and WBCF for some trusted code that we expect to behave reasonable, e.g.\ by treating return seals in a reasonable way.
This means that it is safe to give return seals to trusted code; but at the same time, we have some code that we do not trust and that we want to guarantee LSE and WBCF against.
This means that there is a difference between what is safe to give to the trusted code and the untrusted code which we capture by having a trusted and untrusted value relation.
The two value relations are sketched in Figure~\ref{fig:value-relation}.
